\section{Conclusion}
\label{sec:conclusion}

Both in the corpus study (Section~\ref{sec:corpusstudy}) and the split-100 experiment (Section~\ref{sec:split100experiment}), we found evidence that writers prefer to use a PL when N1 necessarily has a plural interpretation due to compound-internal semantics (internal plural effect).
We found no evidence for a similar influence of a plural suffix on the whole compound (external plural effect).
The latter effect could either have been semantically motivated in some cases or be a simple compound-internal number agreement tendency, neither of which appear to be the case.
In light of the suspicions raised in the literature that there might be plural effects within German compounds, as well as the previous research on Dutch linking elements (see Section~\ref{sec:pluralinterpretationofpluraliclinkagesingermananddutch}), our results do not come as a surprise.
Regardless of the diachronic development of linking elements, writers use PLs as cues to the interpretation of N1+N2 compounds (see also \citealt[212]{BangaEa2013b}).
The form of an N1 with a PL is one which writers associate strongly with semantic plurals, and it appears that they do so also when that form occurs in a compound.
A detailed look at our results reveals more about the actual mechanisms at work.

First, the effect strengths in the corpus study were weak to intermediate, and while the observed effect was clearer in the split-100 experiment, we are nowhere near a categorical split.
There is also substantial per-speaker variation and uncertainty.
(Readers can revisit Figure~\ref{fig:conditions} and Figure~\ref{fig:participants} to convince themselves that this is the case.)
So, we have to answer the question of why the overall effect is not stronger.
As pointed out in Section~\ref{sec:pluralinterpretationofpluraliclinkagesingermananddutch}, \textcite[45]{BangaEa2013a} suggested that there may be a general tendency to avoid linking elements, based on the finding by \textcite{LibbenEa2002} that compounds with linking elements come with higher processing costs.
This could account for the high percentage of zero linking elements (see Section~\ref{sec:databaseandproductivityassessment}, especially Table~\ref{tab:freqoverview}).
Furthermore, regardless of whether one favours a rule-based or a similarity\slash exemplar-based view (see Section~\ref{sec:conditionsonlinkageselectioningerman}), in many cases the use of a PL is highly unlikely for unrelated reasons such class membership or phonotactics.
A clear case are words ending in full vowels, which have an \textit{-s} plural but resist \textit{-s} linking elements strongly.
For example, \textit{Auto-s+kollektion} `car collection' is very unexpected -- according to some sources, even impossible \citep{Wegener2003,Wegener2005,Fuhrhop1996} -- and \textit{Auto+kollektion} would be preferred by a huge margin.
Such factors stand in the way of establishing a stronger link between PLs and plurality.

Second, we must ask why the corpus-based results were weaker than the split-100 results.
We propose that this is due to the fact that we made a considerable effort to ensure that the items in the experiment consisted of compounds which were most likely novel to the subjects (see Section~\ref{sec:designchoiceofstimuliandparticipants}).
In creating the samples for corpus study, however, we did not differentiate between compounds strongly established in language use and novel compounds.
Therefore, the corpus sample contains lexicalised compounds with conventionalised idiosyncratic linking elements.
Of course, we would expect that even lexicalised compounds follow the tendency to associate PLs with plural meaning at least to some extent.
Thus, simply filtering compounds which have a high token frequency from concordances could obscure part of the picture and may not be in our best interests when trying to study this phenomenon.
More theoretical, empirical, and even methodological work on this is clearly required.

Third, we must ask why PLs differ with respect to their tendency to be used to mark plurality in the corpus study.
(The number of possible stimuli in the experiment was too low due to constraints imposed by the experimental procedure to allow a more differentiated look at variation between PLs.)
The order of preference established in Section~\ref{sec:corpusstudy} (especially Figure~\ref{fig:corpuseffects}) was \textit{=e} $\gg$ \textit{=er} $\gg$ \textit{-er} $\gg$ \textit{=} $\gg$ \textit{-e} $\gg$ \textit{-en} $\gg$ \textit{-n}.
The strength of the internal plural effect is thus by and large negatively correlated with the type frequency of nouns which take the respective plural (see Section~\ref{sec:databaseandproductivityassessment}, especially Table~\ref{tab:freqoverview}, and Section~\ref{sec:queries}, especially Figure~\ref{fig:corpusselection}).
Additionally, the inflectional suffixes \textit{-en} and \textit{-n} occur in many positions in German nominal inflection and therefore provide the lowest cue validity for plurality.
For example, there is a dedicated dative marker \textit{-(e)n} attaching to all plurals except \textit{-(e)s}, where it is excluded for phonotactic reasons.
Also, weak nouns mark all non-nominative singular forms with \textit{-(e)n}.
Finally, the so-called \textit{weak} and \textit{mixed} adjectives end in \textit{-en} in all oblique (dative and genitive) singular forms and the masculine accusative singular.
On the other hand, \textit{-er} is much more exclusively a plural marker (with some exceptions in the so-called \textit{strong} adjectival paradigm), and umlaut is clearly reserved to mark plural in German nominal inflection.%
\footnote{Some comparative and superlative adjectives take an umlaut in addition to the corresponding suffixes, but the formation of comparatives is clearly something very different from case and number inflection.
Also, case and number inflection attaches additionally to the right of the comparative suffix.}
In short, stem umlaut is a highly salient cue, whereas \textit{-e} (schwa) and \textit{-(e)n} (usually realised as a syllabic nasal) are the least salient of plural markers.
Taken together, this means that plural interpretation of PLs is stronger with what \textcite{Koepcke1993} calls a higher \textit{Signalstärke} `signal strength' of the PL as a plural marker.
His criteria for high signal strength are high salience, high validity, low type frequency, and a high degree iconicity.%
\footnote{We do not discuss the more complicated notion of iconicity here for reasons of space.
By type frequency, Köpcke means the number of different forms in a paradigm, and what we have described as cue validity above encompasses Köpcke's validity and type frequency.
For us, type frequency is rather the number of different nouns with which a plural marker occurs.}
We conclude that writers associate plural meaning more strongly with PLs if the PL itself is more strongly associated with plurality, \ie has greater signal strength.
Furthermore, we consider it likely that the correlation between type frequency in our sense and the increased tendency for plural interpretation of PLs is merely accidental.
The more salient and cue-valid plural patterns happen to be the less type-frequent ones for historical reasons.

Fourth, an explanation of why only the internal plural effect was observed is necessary.
In Section~\ref{sec:linkingelementsinprobabilisticmorphology}, we argued that restrictive frameworks tend to elevate universal tendencies to hard universal constraints.
Among the proposed morphological constraints were those requiring that there be no inflection inside products of word formation.
We would like to point out that the tendencies that we have uncovered concern the internally licensed inflectional category of number only (see Section~\ref{sec:pluralinterpretationofpluraliclinkagesingermananddutch}).
We found no evidence that case marking occurs on N1, nor are we aware of any such evidence.
Case could conceivably only be used to specify the grammatical relation between a compound's constituents, and this is something not usually found in compounds, but rather in complex noun phrases.
Number, on the other hand, has nothing to do with the grammatical relation between the constituents.
Writers use the optional plural marking when the individual and joint conceptual representation of the constituents allows this, but it has nothing to do with syntagmatic grammatical relations.
However, the external plural effect would require that a formed compound be somehow transparent for grammatical categories attaching to its whole.
This is atypical of compounds.

Fifth, we would like to propose an explanation of why our findings seemingly contradict those of \textcite{KoesterEa2004}.
They show in an experiment using event-related potentials (ERP) that mismatches between the semantic (non-)plurality of N1 and PLs\slash NPLs do not lead to the expected N400 effect, concluding that PLs and NPLs are not used by hearers to decode the conceptual structure of N1+N2 compounds.
In contrast to the ERP experiment, we only considered the production side of the effect by looking at usage data from a corpus and preferences in a production-oriented decision task.
Since plurality is only marked optionally within compounds, as we have argued extensively above, hearers cannot and need not rely on PLs as plural markers.
However, the fact that hearers do not rely on plural marking does not necessarily prevent writers from using plural forms where a plural meaning is intended.
This, then, raises the question of whether the plural is really \textit{marked} or just redundantly indicated by a PL.
Only further research can shed light on such questions.%
\footnote{Some relatively simple experiments could provide clarification about the reception of PLs.
These could involve subjects associating objects or illustrations with truly ambiguous compounds such as \textit{Apfel+teller} `apple plate' and \textit{Äpfel=+teller}.
For more implicit testing, the task might be set up in the visual world paradigm.}

Sixth and finally, \textcite{BangaEa2013a} found that German L2 learners of Dutch do not react as strongly to the Dutch PL \textit{-en} as Dutch L1 speakers.
This could be due to the fact that, as we have shown and explained, Germans attribute the lowest plural interpretability to \textit{-en} in German, rather than due to an across-the-board weakness of the relationship between plurality and PLs in German, as the authors speculated \parencite[45]{BangaEa2013a}.
If there really is an interference effect from the German L1, then the Dutch marker being accidentally identical to the German marker with the lowest signal strength would naturally lead to low affinity for a plural interpretation in compounds.
For Dutch speakers, however, given the complete absence of nominal case inflection and much reduced system of plural markers, differences in signal strength are irrelevant.

In conclusion, our study has helped to show that German PLs can indeed have a plural interpretation.
More importantly, we have shown that there are differences in when this interpretation is available: primarily, when the head of the compound is a collective noun.
This forces a plural interpretation upon the N1 which represents multiple members of this collective, and this plural intepretation is reflected in an inclination toward the interpretation of a pluralic linking element as a plural marker.
We have also provided cognitively oriented explanations for why the plural interpretation is available in some situations and not others.
We see many possible routes for future research on the subject.
For example, more refined corpus studies taking into account the degree to which a compound is novel or established should be made.
Also, the differences between the production and the reception side of plurality in compounds need further research, especially considering that for each side, only one study has been conducted (namely \citealt{KoesterEa2004} and this one).
While there appears to be a solid connection between PLs and plurality, this connection's exact nature still remains to be characterised fully.
