\section{Linking elements in German}
\label{sec:linkingelementsingerman}

\subsection{The form and distribution of linking elements in German}
\label{sec:theformanddistributionoflinkingelementsingerman}

\subsubsection{German linkages}

In this paper, we exclusively deal with determinative (endocentric) nominal compounds, \ie compounds formed through the concatenation of two constituent nouns (possibly with intervening linking elements, see below) where the second noun (N2) is the head modified by the first noun (N1).
While compounding is a recursive process in principle, we ignore complications involved with more complex structures and look only at binary compounds.
We refer to these structures as \textit{N1+N2 compounds}.

In the majority of such compounds in German, N1 and N2 are simply concatenated, and N1 appears in its base (uninflected) form, which is identical to at least the nominative singular form.
A linking element (LE), as mentioned above, is optional segmental material inserted between N1 and N2.
LEs in compounds are not exclusive to German; see \textcite{SchreuderEa1998,BangaEa2013a,BangaEa2013b} on Dutch LEs.%
\footnote{See also \textcite[27]{KrottEa2007} for a typological overview of some systems of compound infixoids.
%We resist the temptation of equating structures across languages too hastily and restrict our review to Germanic languages with highly similar systems.
%For example, in \textcite[4]{KirchnerNicoladis2009} (citing \citealt{Spencer1991}, page numbers not specified), it is claimed that in Turkish ``a variety of inflectional suffixes can appear within compounds'' (according to the glosses including a possessive suffix \textit{-i} and a putative person marker \mbox{\textit{-um}}), linking these to Germanic LEs.
%They cite an example \textit{vurd-um duy-maz}, which is lexicalised and always spelled \textit{vurdumduymaz}.
%First, the appropriate segmentation would be \textit{vur-du-m} with \textit{vur} `hit', \textit{-du} PRT, and \textit{-m} \textsc{1SG} and \textit{duy-maz} with \textit{duy} `feel', \textit{-maz} INF-NEG.
%It is a chunk fossilised as a word with an original literal meaning of roughly `I hit, not feel', now meaning `thick-skinned'.
%The construction which \textcite[313--319]{Spencer1991} mainly discusses, however, the izafet construction (with its marker \textit{-i}) embedded in units that resemble compounds.
%The izafet construction is arguably more phrasal than true word formation processes.
%All the examples are thus very different from Germanic N1+N2 compounds with LEs and might be more similar to compounds with phrasal first constituents such as \textit{do or die situation} (see \citealt[366]{Olsen2015}), where surely different regularities apply.
}
However, German speakers use an unusually high number of different LEs, and they also make other types of changes to the base form of N1 (in order to refer to linking elements together with other formal changes to N1, we will use the umbrella term ``linkage'').%
\footnote{Linkages in German have developed diachronically from inflectional forms, see \textcite{NueblingSzczepaniak2013,Szczepaniak2016}.}
The list of segmental LEs is widely accepted to be: \textit{e}, \textit{er}, \textit{s}, \textit{es}, \textit{n}, \textit{en}, \textit{ns}, and \textit{ens} (see \citealt[31]{Neef2015}, \citealt{KrottEa2007}).
The elements \textit{e} and \textit{er} can occur together with an optional umlaut on N1, and some compounds only have umlaut on N1 and no segmental LE at all.
Also, certain LEs can replace N1-final segments.
Lastly, N1s ending in schwa (graphemically \textit{<e>}) can drop this schwa in compounds.

Before we continue, a few notes on the notation we use in this paper: 
We will not mark zero linking elements as, for example, $\varnothing$, but rather represent the simply concatenated compounds as N1+N2 without anything in between. 
We will represent a linking element \textit{X} attaching to N1 as \textit{-X}, and \textit{=X} will denote a LE attaching to N1 with additional umlaut in N1.
An umlaut-only linking element is indicated by \textit{=} alone.
The special notation \textit{*e} is used for deletion of the final schwa of N1.
Furthermore, \textit{+} separates N1 (possibly with LE) and N2 in our analyses.
Graphemically, however, German compounds are usually spelled as one word; the segmentation is intended purely as a reading aid.%
	\footnote{Some compounds, for example those involving names or loan words, are sometimes written with a hyphen, such as \textit{Adenauer-Zeit} `Adenauer period'.
	We exclude them from our study because they virtually never occur with LEs and have specific compound-internal semantics.
	There are also occasional spellings of compounds as two words such as \textit{Blumen Welt} `world of flowers' and with in-word capital letters such as \textit{BlumenWelt}, which are much debated from a normative perspective (see also \citealt{Scherer2012}).
	These spellings are assumed to be specific to certain genres (such as adverts) and are quite rare overall.
	Therefore, we do not include them in our study.}
Table~\ref{tab:linkages} illustrates the different types of linking elements in German.%
	\footnote{Linking elements are also found in other sorts of German compounds, for example N+A compounds such as \textit{herzensgut} (\textit{Herz-ens+gut}) `kindhearted', \textit{lebensfreundlich} (\textit{Leben-s+freundlich}) `life-sustaining\slash livable', or \textit{hundelieb} (\textit{Hund-e+lieb}) `dog-loving'.
	While their distribution, function, and interpretation in such compounds might be related to that in N1+N2 compounds, our studies reported in Sections~\ref{sec:corpusstudy} and~\ref{sec:split100experiment} make use of diagnostic features exclusive to N1+N2 compounds, and we therefore excluded all other types of compounds.}

\begin{table}[htbp]
  \resizebox{\textwidth}{!}{
    \begin{tabular}{lllll}
    \toprule
    Linkage & Pl & example & literal gloss & translation \\
    \midrule
    $\varnothing$    && \textit{Haus+tür}                & house door       & `front door' \\
    -s   &            & \textit{Anfang-s+zeit}           & beginning time   & `initial period' \\
    -n   & \Checkmark & \textit{Katze-n+pfote}           & cat paw          & `cat's paw' \\
    -en  & \Checkmark & \textit{Frau-en+stimme}          & woman voice      & `female voice' \\
    *e   &            & \textit{Kirsch*kuchen}           & cherry cake      & `cherry cake' \\
    -e   & \Checkmark & \textit{Geschenk-e+laden}        & gift store       & `gift store' \\
    =e   & \Checkmark & \textit{Händ=e+druck}            & hand press       & `handshake' \\
    =    & \Checkmark & \textit{Mütter=+zentrum}         & mother centre    & `centre for mothers' \\
    -er  & \Checkmark & \textit{Kind-er+buch}            & child book       & `children's book' \\
    =er  & \Checkmark & \textit{Büch=er+regal}           & book shelf       & `bookshelf' \\
    -ns  &            & \textit{Name-ns+schutz}          & name protection  & `name protection' \\
    -ens &            & \textit{Herz-ens+angelegenheit}  & heart matter     & `affair of the heart' \\
    \bottomrule
    \end{tabular}
  }
  \caption{Overview of the different linkages in German nominal compounds; \textit{=} is used to denote LEs which trigger umlaut on N1, \textit{*e} denotes linkages where the final schwa of N1 is deleted; the column labelled \textit{Pl} indicates whether the linkage is (in most cases) formally identical to the plural of N1 (see below)}
  \label{tab:linkages}
\end{table}

Whether \textit{-en} and \textit{-n} or \textit{-ens} and \textit{-ns} should be described as allomorphic variants (\ie \textit{-(e)n} and \textit{-(e)ns}) is debated.
See Sections~3.2 and~3.6 of \textcite{NueblingSzczepaniak2013} for an argument in favour of this view and \textcite[33--36]{Neef2015} for an argument against it.
This issue does not affect our study, and we separate the two potential allo-forms in order to maximise the informativity of our results.
Since we do not look at linkages with \textit{-s} and \textit{-es} in detail, however, we have conflated these two into \textit{-(e)s}, although this should not be equated with referring to them as allomorphs, which they are not (cf.\ \citealt[81]{NueblingSzczepaniak2013}).
This was done simply for ease of exposition, since \textit{-es} cannot be a plural suffix and, although \textit{-s} can be, it is avoided within compounds after N1s that take \textit{-s} as their plural suffix (cf.\ \citealt{Wegener2003,NueblingSzczepaniak2013}).

The different linkages have quite different frequencies, with the zero and \textit{-(e)s} linkages being by far the most frequent ones.
For example, \textcite[177]{Gallmann1998} reports that $70\%$ of all N1+N2 compounds have zero linkage (not specifying whether he refers to type or token frequency).
\textcite[29]{KrottEa2007} report that the compound types with zero linkage make up $65\%$ of all compounds in the CELEX database.
%See Section~ \ref{sec:databaseandproductivityassessment} for a detailed breakdown of the type and token frequencies in the 21 billion token DECOW16A corpus.

Finally, it should be mentioned that in some terminologies, LEs would not be called LEs when they are actual plural markers (\ie when plural form of the LE and plural meaning of N1 occur together).
We follow the liberal choice of words by \textcite{BangaEa2013b}, who also call the respective affixes ``linking elements'' whether or not they mark plural meaning (see \citealt[196]{BangaEa2013b} for a discussion of stricter views).

\subsubsection{Conditions on linkage selection in German}
\label{sec:conditionsonlinkageselectioningerman}

The choice of linkage in any given compound is not fully predictable, but the grammatical gender of N1, its declension class (dependent largely on gender), its phonotactics, and possibly plural semantics all limit the options significantly (see \citealt{Fuhrhop1996,NueblingSzczepaniak2013}).
All these morpho-phono\-logical and lexical factors which partially determine the choice of linkage are based on N1, so the distribution of linkages in general is unanimously treated as suffixation of N1.

Several (soft) descriptive generalisations concerning linkage distribution can be made (cf.\ e.g.\ \citealt{Fuhrhop1996} and \citealt{NueblingSzczepaniak2013} for extensive overviews).
Derived nouns ending in suffixes like \textit{-ung}, \textit{-heit}, \textit{-tum}, etc.\ have a strong tendency to occur with an \textit{-s} linkage, as in \textit{Heizung-s+wartung} `heating maintenance'.
Simplex masculine and neuter nouns are those which often take the \textit{-(e)s} LE, in which case the form is identical to the genitive singular, for example \textit{Boot-s+fahrt} `boat trip' (with neuter \textit{Boot}) or \textit{Tag-es+form} `form of the day' (with masculine \textit{Tag}).
Also, N1s ending in full (non-reduced or tense) vowels such as \textit{Oma} `grandma' or \textit{Auto} `car' can never take the \textit{-s} LE (although \textit{-s} is their only inflectional suffix when they are used as independent nouns) and tend to occur with a zero linkage as in \textit{Auto+wäsche} `car wash'.
See \textcite{Wegener2003} and \textcite{FuhrhopKuerschner2015} for further discussion of the \textit{-s} linkages and \textcite{Fehringer2009} for an investigation of an emerging \textit{-s} PL in northern German dialects.
Furthermore, feminine nouns ending in schwa virtually always occur with the linking element \textit{-n} \parencite[32]{LibbenEa2002}, which is also their plural morpheme.
So-called weak masculine nouns and so-called mixed masculine and neuter nouns, which have an \textit{-(e)n} plural, often occur with an \textit{-(e)n} LE, \egg \textit{Linguist-en+witz} `linguist's joke\slash joke about linguists' and \textit{Schwede-n+humor} `Swede humor'.%
\footnote{For weak nouns, the \textit{-(e)n} LE is also identical to all non-nominative-singular forms, because they follow an otherwise unusual paradigm where the nominative singular is unmarked and all other forms are marked identically with \textit{-(e)n} (see \citealt{Koepcke1995,Schaefer2016c}).}
Finally, \textit{-ens} and \textit{-ns} are idiosyncratic and rare, used only with a handful of N1s.

More systematically, \textcite{DresslerEa2001} showed in a cloze test that the choices German native speakers make with respect to linkages in novel compounds are partially predictable from rules, but that an analogical component (similarity to existing compounds with the same first constituent) is required.
The approach in \textcite{KrottEa2007} shows how a model with very high explanatory power can be constructed completely without rules and exceptions, based only on analogy.
Using an implemented exemplar-based model, experimental validation, and post-hoc analysis, they find that the choice of linkages in novel compounds can be predicted well by considering exemplar families of compounds that have the same N1 together with features of the first constituent such as rime, gender, and inflectional class \parencite[47]{KrottEa2007}.

In sum, the zero linkage can be considered a sort of default, since it is the most frequent form of linkage in N1+N2 compounds and no compound is phonologically unacceptable with a zero linkage.
When a LE does appear, which form it takes is affected primarily by N1.
N1s have certain preferences for linkage selection, and they also often disprefer particular linkages (partially depending on gender, stem-final segments, and the derivational status of N1).
There is solid evidence that exemplar effects can account for most selection tendencies.
It remains a noteworthy fact, however, that except for the zero and \textit{-(e)s} linkages, the linkages which N1s can take are almost always identical to their plural markers.

\subsubsection{Alternations between linkages}

Despite the existence of more or less firm constraints on the selection of linkages, which linkage will be chosen in a given compound is by no means fully pre-determined.
Dating back to \textcite{Augst1975}, alternations between one or more different linkages with the same N1 have been described.
Alternations with more than two alternatives are rare, however.
\textcite[134--135]{Augst1975} reports that among the $4,025$ N1s he examined, $390$ occurred with two linkages, $31$ with three, and only eight with four.
Notice that the proportion of N1s occurring with two different linkages is considerable at $9.7\%$.
We propose that corpora containing more liberal usage of language which is not strongly bound by norms combined with contemporary technologies of large-scale automatic analysis will reveal many more N1s occurring in at least a two-way alternation between a zero linkage and a pluralic linkage (see Section~\ref{sec:data} and Section~\ref{sec:corpusstudy}).

Some researchers are skeptical towards the idea of productive alternation.
At the other extreme, roughly forty years after Augst's study, \textcite[31]{NeefBorgwaldt2012} and \textcite[46]{Neef2015} suggest that for each N1, there is only one productive and uniquely determined linking element.
They treat all cases of alternation as lexicalised ``exceptions''.
In \textcite[42]{NeefBorgwaldt2012}, when confronted with apparently alternating linking elements for the N1 \textit{Ohr} `ear' (in the normative spelling dictionary \textit{Duden} \citealt{Duden2006}, they found $19$ compound types with a pluralic linking element (\textit{Ohr-en}) and $15$ with no linking element), the authors conclude not that these forms alternate (a position at odds with Augst), but that ``the method does not result in a clear picture about the productive form of the first constituent'' and that there might simply be a ``a developing allomorphy of the first constituent for this particular lexeme''.%
\footnote{``Damit liefert die vorgeschlagene Methodik kein klares Bild zur produktiven Vordergliedsstammform.
	Denkbar ist allerdings, dass sich für dieses spezielle Lexem eine Allomorphie auf der Ebene der Vordergliedsstammform herausgebildet [\ldots]'' \parencite[31]{NeefBorgwaldt2012}}
With such an analysis, one runs the risk of obscuring potentially interesting patterns in the data.
Furthermore, although the authors refer to their approach as a ``corpus study'', in light of contemporary methods in corpus linguistics, this methodology could be improved upon.
Dictionaries may certainly be used to study spellings and the prescriptive standard, but a more principled and descriptive approach to assessing productive linking element alternation delivers deeper insight into the phenomenon as it really occurs.
We discuss such an approach in Section~\ref{sec:data}.


\subsection{Linkages as plural markers}
\label{sec:linkagesaspluralmarkers}

\subsubsection{Plural interpretation of pluralic linkages in German and Dutch}
\label{sec:pluralinterpretationofpluraliclinkagesingermananddutch}

Our study focusses on N1s which alternate between a pluralic and a non-pluralic linking element, and it is our goal to show that these linking elements actually have a plural interpretation and to clarify when this appears.
If they do have a plural interpretation, then at least in some compounds, the linking element is a case of plural inflection inside a compound.
We now review some of the research on a potential plural interpretation of pluralic linking elements.
We will first consider theoretical and empirical approaches to this question for German compounds, followed by the more advanced research on this question that has been conducted for Dutch.

An extreme theoretical position with respect to any functional or semantic interpretation of linking elements is espoused by \textcite{NeefBorgwaldt2012} and \textcite{Neef2015}.
In these papers, the authors state that linking elements cannot be functional, since no one proposed function (for instance, to provide a conceptual boundary between constituents, cf.\ \citealt[530]{Fuhrhop1996}; to close an open syllable ending on schwa, cf.\ \citealt[446]{Wegner2003}; or a potential function as a plural marker, cf.\ \citealt[534]{Fuhrhop1996}, \citealt[427]{Wegner2003}) holds strictly for all linking elements across the board. 
The plural marking function is not strict insofar as a pluralic linkage is not required for N1 to be interpreted as a semantic plural, and a pluralic linkage also does not reliably exclude a singular interpretation.
While this in no way excludes the possibility that a pluralic linkage is a soft cue for plurality, the authors seem to suggest that function\slash meaning and form have to stand in a one-to-one relationship, except for a small number of exceptions which have been lexicalised (\egg \citealt[42]{NeefBorgwaldt2012}).
They dismiss polyfunctional (and thus multifactorial) explanations altogether, because no stringent system of functions has been proposed which explains exactly under which conditions which linkage is chosen (\egg \citealt[27--29]{NeefBorgwaldt2012}).
Such a view (similar to the dual-route approach as discussed in the context of LEs in \citealt{KrottEa2007}) has become less and less tenable in the face of recent research on the nature of the form--meaning relationship in morphology, which paints a clearly probabilistic picture where more often than not, similarity relations play a major role (see \citealt[107]{ArndtlappeEa2016}).
The present study adds to the evidence that such categorical and exceptionless approaches are inadequate with regard to the interpretation of German linking elements.

%More substantially, it was shown in \textcite{KoesterEa2004} that in the perception of spoken German compounds, hearers do not use pluralic linking elements as cues to plural semantics.
%However, much like \textcite{SchreuderEa1998} argue for effects of plural semantics in written Dutch compounds (to be discussed in more detail below), the picture might be different for written German.

Theoretical approaches to the question of the possibility of inflection within compound boundaries also display conflicting perspectives. 
For instance, \textcite[9]{Schluecker2012} states that there can be no inflection on non-heads in compounds, because these non-heads either do not inflect at all or the suffixes with which they occur (\ie linking elements) are non-inflectional by definition.
This approach is another example of a framework turning tendencies into hard-and-fast constraints, which may obscure the true nature of the multifaceted phenomenon in question.
Furthermore, this perspective depends greatly on one's analysis of the characteristics of linking elements and on which type of inflection one considers.
While it is true that, for instance, linking elements no longer represent genitive case inflection like they originally did, we will show that linking elements should not be considered non-inflectional as concerns number.
Indeed, this more liberal distinction is made by other scholars as well.
\textcite[577]{FuhrhopKuerschner2015}, for example, state in their survey of linking elements in Germanic languages that ``the expression of number by linking elements generally seems possible'', while case marking, another instance of inflection, is mostly considered to be unavailable within compounds.
Furthermore, \textcite[178--180]{Gallmann1998} distinguishes between internally licensed and externally licensed inflectional features.
%He adopts a specific formulation within the Government and Binding framework, but we focus on the gist of his generalisation, which can be expressed well outside of that specific framework.
According to him, externally licensed inflectional features are those which are determined by the syntagmatic context in which a noun occurs, such as case assignment by verbs.
Internally licensed features, on the other hand, are those which are assigned not by context, but by categorial membership (such as grammatical gender) or interpretation (such as plurality).%
%\footnote{An example of a non-free plural according to \textcite[179]{Gallmann1998} would be the plural on \textit{students} in \textit{Dale and Daryl are students}.
%See his parallel German example (4b).
%}
Gallmann maintains that externally licensed inflectional features -- prominently, case -- cannot be assigned to non-heads in compounds (N1s), but he does not explicitly exclude internally licensed features like plural marking on N1s.
Thus, the possibility of plural marking within German compounds remains, at least for some, theoretically open.

Interestingly, however, it was shown in \textcite{KoesterEa2004} that in the perception of spoken German compounds, hearers do not use pluralic linking elements as cues to plural semantics.
While this is a substantial finding in support of the impossibility of pluralic linking elements, the picture may very well be different for written German (much like \citealt{SchreuderEa1998} argue for effects of plural semantics in written Dutch compounds).

These examples, though far from all comments made on this topic, illustrate the divide among linguists and grammarians of German.
Considering this divide, astonishingly little empirical research has been published on the question.
However, for Dutch, there exists a decades-long tradition of substantive experimental research into plural interpretations of pluralic linkages.
\textcite{SchreuderEa1998} and \textcite{BangaEa2012} demonstrate how a change in the official Dutch orthography, which assimilated the LE to the plural marker graphemically, fostered the plural interpretation of non-heads of compounds in written Dutch.
Also, \textcite{BangaEa2013a} show that a plural interpretation of N1s in novel Dutch compounds is positively linked to the occurrence of the optional LE \textit{-en}, which is homophonous with the plural marker.
First, they show that subjects prefer to use \textit{-en} with N1 in contexts where a plural meaning of N1 was made clear.
Second, they demonstrate that the preference for the pluralic linking element is even activated when the compound contains a singular form of N1 but when the context creates a plural meaning for N1, which is evidence that the connection between the LE and plurality is not just based on a formal recency effect.
They confirm that plural interpretation indeed creates a preference for using \textit{-en}, but that form-based repetition effects strengthen the meaning-based effect \parencite[45]{BangaEa2013a}.

Third and of special relevance to our study, they also test German L2 learners of Dutch and find that for them, the plural effect is weaker than for native speakers of Dutch.
They offer several possible interpretations for this \parencite[45--47]{BangaEa2013a}.
Citing \textcite{LibbenEa2002}, who show that linking elements in German come with a processing overhead, they speculate that German speakers might have a tendency to avoid linking elements.
Also, they propose that since German plurals are not always marked (there is a zero plural in German, just as there is a zero linking element), German speakers might associate linking elements less strongly with plurality.
Finally, they argue that plural markers in German are sometimes formally identical to case markers, which could also weaken the connection German speakers establish between plurality and linking elements.
We return to these ideas in Section~\ref{sec:conclusion} after having presented our own results.

In \textcite{BangaEa2013b}, the authors compare the interpretation of Dutch compounds by native speakers of Dutch to the interpretation of conceptually identical English compounds by English native speakers.
They compare plurality ratings for conceptually plural N1s, \ie those where a plural meaning of N1 is a de-facto necessity, to plurality ratings for conceptual non-plurals.
Their examples include \textit{bananenschil} `banana peel' for a conceptual non-plural and \textit{aardbeienjam} `strawberry jam' for a conceptual plural.
In essence, they show that Dutch speakers produce higher plurality ratings for compounds with \textit{-en} and lower plurality ratings for compounds without \textit{-en} for both groups of compounds (conceptually plural and non-plural) compared to English native speakers for the English compounds identical in meaning and structure.
That is, the LE provides Dutch speakers with an additional cue for plurality, independent of the cues coming from the conceptual structure of the compound.
In a second experiment, they show that Dutch subjects as L2 speakers of English react to English compounds by and large like English speakers (for a report of some complications, see \citealt[211]{BangaEa2013b}).
This corroborates findings that the actual presence of the linking element is a key cue for plural interpretation for Dutch speakers.


\subsubsection{Consequences of plural linkages for morphological theories}
\label{sec:consequencesofplurallinkagesformorphologicaltheories}

A crucial point in the discussion of inflection within compounds is whether frameworks and theories can deal with it appropriately, as we mentioned above.
In theories ranging from the strict layering hypothesis by \textcite{Siegel1979} through the lexical Phonology of \textcite{Mohanan1986} and the a-morphous morphology by \textcite{Anderson1992} to the words-and-rules theory by \textcite{Pinker1999}, it has been maintained that inflection applies after derivational word formation (including compounding), leading to inflectional affixes being positioned farther toward the edges of words than derivational affixes and to inflectional affixes not occurring between constituents of compounds.
This was encoded in the respective theories as hard and putatively universal constraints.
Such approaches were disputed, however, from very early on, for example in \textcite{Bochner1984}, where the author shows how inflection can occur within derivation (see \citealt[2--3]{KirchnerNicoladis2009} for more on this debate).
Most pertinent in the context of our study is the argument in \textcite[47--48]{BangaEa2013a} that such restrictive theories fail to explain how the Dutch LE \textit{-en} can have a plural interpretation (thus being an inflectional suffix) and occur between constituents of compounds (see their results summarised above).
The same would be true for German compounds if pluralic linkages turn out to be plural markers systematically.

However, as \textcite[5]{KirchnerNicoladis2009} correctly point out, strong tendencies (falsely interpreted as universal constraints in older generative morphology) for inflection to appear only at the edges of words should still be explained.
Given this goal, we consider it highly instrumental to describe exactly where and when inflection does \textit{not} appear at the edges of words, and this paper is about such a case (see Section~\ref{sec:conclusion}).
As we have argued in Section~\ref{sec:linkingelementsinprobabilisticmorphology}, frameworks should not impose unnecessary restrictions which stand in the way of describing phenomena as they actually occur.
Furthermore, the inherent probabilistic nature of linguistic phenomena -- most obvious in situations where more than one option is available in a so-called \textit{alternation} -- means that investigating preferences might be more useful than searching for strict rules and lexicalised exceptions.

\subsection{Outline of our study}

Our main hypothesis under investigation is whether a pluralic linkage in a N1+N2 compound is systematically interpreted as a semantic plural by native speakers of German.
We use the term ``systematic'' in the sense of probabilistic grammar, where preferences (under specific given conditions) are not assumed to be binary but probabilistic, weighted, and better described as numerical rather than discrete.
As sources of data, we will use a large corpus and an experimental setup.
Since annotating corpus exemplars reliably for whether the N1 in a compound has a plural meaning is quite difficult in the general case, we isolate two specific and relatively easy-to-detect configurations in which a pluralic linkage might signal plurality, where the second configuration (internal plural) is the one we consider to be the crucial one in showing that pluralic linkages have plural meaning:

\vspace{\baselineskip}

\begin{enumerate}
  \item A plural on the entire compound (formally on the head constituent) might trigger the use of a pluralic linkage.
  We call this the \textit{external plural effect}.
  \item Certain semantic classes of N2s standing in an appropriate semantic relation with N1 might force N1 to have a plural interpretation and therefore lead to a preference for using the pluralic linkage.
  We call this the \textit{internal plural effect}.
\end{enumerate}

\vspace{\baselineskip}

The external plural effect on linkage selection might have two different motivations.
First, there are cases where the referents of N1 necessarily form a set or sum entity with more than one member when the compound as a whole is a plural.
This might lead to a preference of pluralic linkages.
For example, we might see a preference for a compound \textit{Hund+herz} `dog's heart' with the non-pluralic linkage (zero in this case) in the singular but \textit{Hund-e+herzen} `dogs' hearts' with the pluralic linkage (\textit{-e} in this case) in the plural.
It is not necessary to distinguish between different non-pluralic linkages (mainly zero and \textit{-(e)s}).
This effect depends to a large extent on the semantics of both constituents and the compound.
In the case of \textit{Hundherz}, the effect is clear because each dog has exactly one heart, so multiple dogs entail multiple hearts.
With other compounds, such as \textit{Brot+mahlzeit} or \textit{Brot-e+mahlzeit} `bread meal', the picture is blurrier because a single loaf or piece of bread can make several meals, and more than one piece or loaf of bread can be consumed in one meal.
Making matters worse, it could be the generic\slash mass noun meaning of \textit{Brot} which is addressed, in which case plurality does not even make sense.
Since we could not find a way to solve these problems reliably with manual annotation, we treat the external plural effect on a strictly formal level.

The second potential motivation for the external plural effect is a purely formal one; there might simply be plural agreement within the compound.
\textcite{BangaEa2013a} and \textcite{BangaEa2013b} have found that there are effects related to the mere presence of a formal plural of N1 in the context of the compound.
However, the plural on the whole compound might trigger a preference for a pluralic linkage on N1, even if the semantic motivation for the external plural effect does not apply.
Thus, even if we find evidence for an external plural effect, we could not be sure that it is an effect related to plural meaning.

The internal plural effect, on the other hand, is only related to the lexical meanings of the compound's constituents, and it is similar to the conceptual plurals in \textcite{BangaEa2013b}, as discussed above.
Prominently, N2s that provoke this effect might have a collective meaning.
In this case, regardless of the grammatical number of the whole compound, there are necessarily several referents of N1 involved conceptually.
Examples include true collectives like \textit{Kindergruppe} `group of children', metaphorical collectives as in \textit{Zitateregen} `rain of quotations', reciprocals such as \textit{Räderwechsel} `swapping of tyres', or relational N2s as in \textit{Lochdistanz} `distance between (the) holes'.

The external plural condition is weaker both conceptually and in terms of operationalisation, so if pluralic linkages are indeed interpretable as plural markers, we expect to find an effect especially for the internal plural condition.
Interestingly, if we find evidence only for the internal plural effect but not the external plural effect, this would fit within a probabilistic version of previous findings that plurality in compounds is purely conceptual or inherent to N1 and does not depend on the grammatical context of the compound (see discussion above, for example \citealt{Gallmann1998}).

In Section~\ref{sec:corpusstudy}, we study these two specific hypotheses using corpus data.
Then, in Section~\ref{sec:split100experiment}, we examine them in an experimental paradigm (split-100 ratings).
Before we turn to these studies, Section~\ref{sec:data} describes the exploratory work that allowed us to make an informed selection of items for the studies.
It also shows that there is a significant number of N1s alternating between pluralic and non-pluralic linkage, contrary to statements to the contrary in the literature (most prominently \citealt{NeefBorgwaldt2012,Neef2015}).
